%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8.18pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/firhardroslan/}{\Large Muhammad Firhard Roslan}} & Email : \href{mailto:firhard@gmail.com}{firhard@gmail.com}\\
  \href{https://www.linkedin.com/in/firhardroslan/}{https://www.linkedin.com/in/firhardroslan/} & Mobile : +447310407893 \\
\end{tabular*}

\section{Profile}{I am a full-time research student at the University of Sheffield currently in the first year. I will be working in the area of software testing focusing on fuzzing.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Sheffield}{Sheffield, UK}
      {PhD. in Software Testing}{January. 2021 -- Ongoing}
        \resumeItemListStart
            \resumeItem{Research Area}{Fuzzing, Mutation Testing, Search-Based Testing}
            \resumeItem{Areas of Interest}{Improving propagation of fuzzers to find faults, Evaluating NoSQL schema using fuzzing techniques, NoSQL schema integrity.}
        \resumeItemListEnd
    \resumeSubheading
      {University of Sheffield}{Sheffield, UK}
      {Master of Science in Software Engineering;  Grade: Distinction}{September 2017 -- September 2018}
        \resumeItemListStart
            \resumeItem{Courses}{Testing and Verification,  Agile Development, Cloud Computing, Software/Hardware Verification.}
        \resumeItemListEnd
    \resumeSubheading
      {University of Nebraska-Lincoln}{Lincoln, Nebraska, USA}
      {Bachelor of Science in Computer Engineering;  GPA: 3.431/4.000}{August 2014 -- May 2017}
        \resumeItemListStart
            \resumeItem{Courses}{Electrical Circuits, Computer Architecture, Cryptography, Database, Data Structure \& Algorithm}
            \resumeItem{Dean's List}{Fall `14, Fall `15 and Fall `16}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading 
      {Oracle Corporation Malaysia}{Kuala Lumpur, Malaysia}
      {Software Engineer}{May 2019 - December 2020}
      \resumeItemListStart
        \resumeItem{Full Stack Developer}
          {Working as a full stack software developer using Oracle JET framework for front-end, Spring Boot for the back-end, and Oracle Database for storing data. Following the right Software Principles.}
        \resumeItem{Sustaining Engineer}
          {Maintaining legacy system particularly related to Oracle Database and payment transactions.}
      \resumeItemListEnd

    \resumeSubheading
      {The OAK Group, University of Sheffield}{Sheffield, UK}
      {Research Software Engineer}{September 2018 - January 2020}
      \resumeItemListStart
        \resumeItem{Full Stack Developer}
          {Full stack NodeJS web developer focusing on real-time video chatting using SocketIO and WebRTC, storing information in MongoDB, handling deployment of NodeJS}
        \resumeItem{Android Developer}
          {Develop native Android application that would communicate with NodeJS for video chatting.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Cybersecurity Malaysia}{Kuala Lumpur, Malaysia}
      {Internship}{September 2018 - January 2020}
      \resumeItemListStart
        \resumeItem{Security}
          {Analyze statically and dynamically vulnerabilities on a website.}
        \resumeItem{Software Principle}
          {Learn good security development standards and practices.}
    \resumeItemListEnd

    \resumeSubheading
      {University of Nebraska-Lincoln}{Lincoln, Nebraska, USA}
      {Undergraduate Teaching Assistant for Embedded System Module}{January 2016 - May 2016}
      \resumeItemListStart
        \resumeItem{Teaching Assistant}
          {Assisted  students with the task at hand and grading, held consulting hours for students.}
        \resumeItem{Lab Assistant}
          {Help students related to Arduino and most of the sensors.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Accomplishment and Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{MSc. Dissertation (with Distinction): Ridesharing for Self Driving Car}
      {Focus on the scheduling of the self-driving car, shortest path optimization.Firebase as web service, Graphhopper as routing engine, OpenStreetMap as the  web mapping service. }
    \resumeSubItem{NIMBUS Lab}
      {Served as a web developer (back-end) on Extensible UAV Interface for Nebraska Intelligent MoBile Unmanned Systems (NIMBUS) lab for senior design project}
    \resumeSubItem{Honer Society}
      {Tau Sigma Honor Society, University of Nebraska-Lincoln}
    \resumeSubItem{Scholarship Awarded}
      {Global Ambassador Scholarship Award, University of Nebraska-Lincoln (2014 - 2017) \&
      MARA GrEP PhD Program, Malaysian Government (2021 - 2025)}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
        {JavaScript, Java, Ruby, C, No-SQL, SQL, currently learning Go}
    \resumeSubItem{Technologies}
        {React, Oracle-JET, MongoDB, SQLite, Git, Firebase, VS Code, Socket IO, IntelliJ, Eclipse}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
